\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
repositioned the example traj feats

@@

\begin{figure}
\centering
\begin{tabular}{c|p{0.4\columnwidth}p{0.4\columnwidth}}
& Low feature-value & High feature-value \\
\hline

\rot{wrist\_tool\_dtw} & 
\adjincludegraphics[trim={.1\width} {.2\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{low}{0}} & 
\adjincludegraphics[trim={.2\width} {.0\height} {.2\width} {.15\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{high}{0}} \\

\rot{tool\_quat\_dist} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{tool_quat_dist}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{tool_quat_dist}{high}{0}} \\

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\end{tabular}

%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\adjincludegraphics[trim={.1\width} {.2\height} {.25\width} {.0\height}, clip, width=\textwidth]{\fta{tool_length}{low}{0}}
%\adjincludegraphics[trim={.1\width} {.0\height} {.25\width} {.0\height}, clip, width=\textwidth]{\fta{tool_quat_dist}{low}{0}}
%\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=\textwidth]{\fta{wrist_bfs_dtw}{low}{0}}
%%\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth, clip=true]{\fta{}{low}{0}}
%(a)
%\end{minipage}
%\hfill
%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=\textwidth]{\fta{tool_length}{high}{0}}
%\adjincludegraphics[trim={.1\width} {.0\height} {.25\width} {.0\height}, clip, width=\textwidth]{\fta{tool_quat_dist}{high}{0}}
%\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=\textwidth]{\fta{wrist_bfs_dtw}{high}{0}}
%%\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth, clip=true]{\fta{}{high}{0}}
%(b)
%\end{minipage}
\caption{Example trajectory snapshots for motions that survey participants rated (a) highly and (b) poorly. In (b) the hand ducks under the table in between the first and middle snapshot.}\label{fig:example_trajectory}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\begin{tabular}{c|p{0.4\columnwidth}p{0.4\columnwidth}}
& Low feature-value & High feature-value \\
\hline
\rot{wrist\_tool\_dtw} & 
\adjincludegraphics[trim={.1\width} {.080\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{low}{0}} & 
\adjincludegraphics[trim={.2\width} {.0\height} {.2\width} {.15\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{high}{0}} \\

\rot{tool\_quat\_dist} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.25\width} {.1\height}, clip, width=0.4\columnwidth]{\fta{tool_quat_dist}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.1\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{tool_quat_dist}{high}{0}} \\

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\end{tabular}
\caption{Trajectory examples of the most useful features, where the feature is displayed row-wise and columns are whether the feature is {\em low} or {\em high} for the example.}\label{fig:example_features}
\end{figure}

@@
